`r glue::glue('Doublet benchmarking results: {params$dataset}')`

### 2024-07-22 analyses/doublet-detection/template-notebooks/02_explore-benchmark-results.Rmd
only calculate metrics if there are sufficient counts, and warn otherwise

```{r functions}
print_doublet_table <- function(df, pred_col, is_ground_truth = FALSE) {
  # Function to print a table of doublet counts and a sentence stating the percentage of doublets
  # df is expected to contain `pred_col`, should should be provided as a string
  dub_tab <- table(df[[pred_col]])
  dub_percent <- round(dub_tab[["doublet"]]/sum(dub_tab), 4) * 100

@@

assess_doublets <- function(df, pred_col) {
  # df is expected to contain columns `ground_truth` and `pred_col`
  # The `pred_col` argument _should_ be provided as a strings

  caret::confusionMatrix(
    # truth should be first
    table(
      "Truth" = df$ground_truth,
      "Prediction" = df[[pred_col]]
    ), 
    positive = "doublet"
  )

>>>>

```{r functions}
print_doublet_table <- function(df, pred_col, is_ground_truth = FALSE) {
  # Function to print a table of doublet counts and a sentence stating the percentage of doublets
  # df is expected to contain `pred_col`, should should be provided as a string

  # If there are no predicted doublets, make sure the tab has a 0 count
  dub_tab <- table( factor(df[[pred_col]], levels = c("singlet", "doublet") ))
  dub_percent <- round(dub_tab[["doublet"]]/sum(dub_tab), 4) * 100

@@

assess_doublets <- function(df, pred_col) {
  # df is expected to contain columns `ground_truth` and `pred_col`
  # The `pred_col` argument _should_ be provided as a strings
  # This function will return NULL if there are insufficient counts to calculate metrics

    # truth should be first
    confusion_table <- table(
      "Truth" = df$ground_truth,
      "Prediction" = df[[pred_col]]
    )

    if (!all(dim(confusion_table) == c(2,2))) {
      print("Metrics could not be calculated; insufficient counts.")
      return(NULL)
    } else {
      return(
        caret::confusionMatrix(
          confusion_table, 
          positive = "doublet"
        )
      )
    }
